Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2018-02-15 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Use download.file instead of bash calls to fetch data

### Summary

@@

### Workspace setup

@@

### GWAS meta-analysis for BMI (included in Boca-Leek)

@@

#### Data download

@@

#### Prune SNPs that are in Linkage Disequilibrium

@@

#### Check Covariate Diagnostics

@@

#### Set up BenchDesign object

@@

#### Run buildBench for the sample size covariate and examine results

@@

#### Run buildBench for the allele frequency covariate and examine results

>>>>

# Summary

@@

# Workspace setup

@@

# GWAS meta-analysis for BMI (included in Boca-Leek)

@@

## Data download

@@

## Prune SNPs that are in Linkage Disequilibrium

@@

## Check Covariate Diagnostics

@@

## Set up BenchDesign object

@@

## Run buildBench for the sample size covariate and examine results

@@

## Run buildBench for the allele frequency covariate and examine results
